Integer Programming Formulations for the Shared Multicast Tree Problem

### 2018-09-26 smt/sec6-strong.tex
MI: some typos fixed

Aiming for stronger LP bounds than those provided by the relaxations of the models introduced in Section \ref{sec:ILP},
this section is devoted to extensions of $\mathcal{X}_2$ and $\mathcal{F}_2$.
Variables with four node indices are added to both models.
Constraints connecting new and original variables then contribute to the improved bounds.

@@

Similarly to the extension $\mathcal{X}_3$ of $\mathcal{X}_2$ by $x$-variables, the model $\mathcal{F}_2$ is extended by variables with four node indices.
Analogously to $A(D)$, let $E(D_0)=E\cap (D_0\times D_0)$ be the set of pairs of \emph{unordered} destination nodes other than $s_0$.
Define variables $f\in\{0,1\}^{A\times E(D)}$, where
$f_{ij}^{st}=f_{ji}^{ts}$ takes the value 1 iff the path in $T^0$ from $s_0$ to $s$ intersects with the path from $s_0$ to $t$ at arc $(i,j)$.
% \newline\newline
% $f^{st}_{ij}=f^{ts}_{ij}=
% \begin{cases}
%     1 & \text{if the paths in $T^0$ from $s_0$ to respectively $s$ and $t$ intersect} \\
%       & \text{at $(i,j)$,} \\
%     0 & \text{otherwise.}
% \end{cases}$
% \newline\newline
%
Variables $f_{ij}^{st}$ can also be regarded as a the \emph{joint flow} from $s_0$ to $s$ and $t$ \citep{Polzin}.
In the cited work, they are successfully used to strengthen formulations for the \textsc{Minimum Steiner Tree} problem.
The new variables enable formulation of an extended model denoted $\mathcal{F}_3$:

>>>>

Aiming for stronger LP bounds than those provided by the relaxations of the models introduced in Section\ \ref{sec:ILP},
this section is devoted to extensions of $\mathcal{X}_2$ and $\mathcal{F}_2$.
Variables with four node indices are added to both models.
Constraints connecting new and original variables then contribute to the improved bounds.

@@

Similarly to the extension $\mathcal{X}_3$ of $\mathcal{X}_2$ by $x$-variables, the model $\mathcal{F}_2$ is extended by variables with four node indices.
Analogously to $A(D)$, let $E(D_0)=E\cap (D_0\times D_0)$ be the set of pairs of \emph{unordered} destination nodes other than $s_0$.
Define variables $f\in\{0,1\}^{A\times E(D)}$, where
$f_{ij}^{st}=f_{ji}^{ts}$ takes the value 1 iff the path in $T^0$ from $s_0$ to $s$ intersects with the path from $s_0$ to $t$ at arc $(i,j)$.
% \newline\newline
% $f^{st}_{ij}=f^{ts}_{ij}=
% \begin{cases}
%     1 & \text{if the paths in $T^0$ from $s_0$ to respectively $s$ and $t$ intersect} \\
%       & \text{at $(i,j)$,} \\
%     0 & \text{otherwise.}
% \end{cases}$
% \newline\newline
%
Variables $f_{ij}^{st}$ can also be regarded as the \emph{joint flow} from $s_0$ to $s$ and $t$ \citep{Polzin}.
In the cited work, they are successfully used to strengthen formulations for the \textsc{Minimum Steiner Tree} problem.
The new variables enable formulation of an extended model denoted $\mathcal{F}_3$:
